---
title: "Make-Changes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Make-Changes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Modify mizerShiny

## Add new plotting functions.

Firstly, you must have your own function, that accepts two `mizerSim` objects and two time arguments. One `mizerSim` object is user ran, the second is the 'base' which we compare against. The values plotted are within this time range. The function must output a ggplot object. 

To put your code in, change the `server` code in *app.R*. Find the section that you wish to change, either following `bioSimData`, `mortSimData` or `fishSimData`, corresponding to the 'Single Species' Biomass and Mortality sections, and the 'Fishery Strategy' section. There will be a repeated section of `output` code where each repeated chunk looks something like this.

```{r, eval=FALSE}
 output$fishspeciesPlot <- renderPlotly({
    req(fishSimData())

    win <- fish_win1()
   
    ggplotly(
      plotSpeciesWithTimeRange(
        fishSimData()$sim1,
        fishSimData()$unharv,
        win$start, win$end
      ))
    )
  })
```

Add you function in place of `plotSpeciesWithTimeRange` and change the output ID, here `fishspeciesPlot`. The `fish_win1()` code reactively takes the user input of the 'Time Range' in 'Fishery Strategy' tab and will rerun this section of code, so keep `win <- fish_win1()` to preserve this reactivity. The `win$start` and `win$end` are the start and end values for the time that is plotted. In the 'Single Species' section, the time inputs are direct from the `input$` provided by the 'Time Range' slider, so copy this functionality from a similar code chunk.

Now you need to add a section in the app for the plot to load to.

Navigate to the `UI` section (faster way is to find an output ID in the same output sequence that you have just added to, and CTRL+F). There will be a section that looks like below, for the biomass, mortality and fishery strategy sections. Wherever you are adding, find the equivalent.

```{r, eval=FALSE}



                          div(
                            class = "plot-card",
                            style = "flex: 4.5; height:50vh; display:flex; flex-direction:column; overflow: hidden; margin-top: -0.5rem",
                            tabsetPanel(
                              id = "fishy_plots",
                              tabPanel(
                                title = "Species",
                                div(style = "flex:1; display:flex;",
                                    plotlyOutput("fishspeciesPlot", height = "100%", width = "100%")
                                )
                              ),
                              tabPanel(
                                title = "Yield",
                                div(style = "flex:1; display:flex;",
                                    plotlyOutput("yieldPlot", height = "100%", width = "100%")
                                )
                              ),
                              tabPanel(
                                title = "Size",
                                div(style = "flex:1; display:flex;",
                                    plotlyOutput("fishsizePlot", height = "100%", width = "100%")
                                )
                              ),
                              if (app_exists("Including", "guilds_information", "checkGuilds", "guildparams_preprocessed.Rdata")) {
                                tabPanel(
                                  title = "Guild",
                                  div(style = "flex:1; display:flex;",
                                      plotlyOutput("fishguildPlot", height = "100%", width = "100%")
                                  )
                                )
                              },
                              tabPanel(
                                title = "Spectra",
                                div(style = "flex:1; display:flex;",
                                    plotlyOutput("spectrumPlot", height = "100%", width = "100%")
                                )
                              ),
                              tabPanel(
                                title = "Diet",
                                div(style = "height:50vh; display:flex;",
                                    plotlyOutput("fishdietsingleplot", height = "100%", width = "100%")
                                )
                              ),
                              if (app_exists("Including", "Nutrition", "checkNutrition", "nutrition.csv")) {
                                tabPanel(
                                  title = "Nutrition",
                                  div(style = "flex:1; display:flex;",
                                      plotlyOutput("nutritionplot", height = "100%", width = "100%")
                                  )
                                )
                              }
                            )
                          )
                        
                              

```

Now copy a `tabPanel` argument, and replace the ID with your new ID.
